Title Goes Here

### 2024-04-22 analysis/paper/paper.qmd
minor update

```{r}
# Carneige Classification
library(googlesheets4)
library(stringi)

CC <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Values1")
Basic2021 <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Data1")

uni_name <- # 550
jobdata %>%  # 550 rows
 select(name_of_hiring_university) %>%
 mutate(name_of_hiring_university = str_replace(name_of_hiring_university, "\\s*\\(.*?\\)$", ""))

view(uni_name)

>>>>

```{r}
# Carnegie Classification
library(googlesheets4)
library(stringi)

# data from https://carnegieclassifications.acenet.edu/resource/2021-update-public-file/
CC <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Values1")
Basic2021 <-
  read_sheet( "https://docs.google.com/spreadsheets/d/1Oe_3X-OR7iuUThb6Tp48prBpbHrWjU4osmHKi1Hbqgc/edit#gid=1922578308",
             sheet = "Data1") %>% 
  # remove a bunch of text from uni names to improve our joins
  mutate(name = str_remove(name, 
                           " Campus Immersion|-Main Campus"))

uni_name <- # 547
 jobdata %>%  # 547 rows
  # remove parentheses and their contents
  mutate(name = str_squish(str_replace(name_of_hiring_university,
                            "\\s*\\(.*?\\)$", 
                            ""))) %>% 
  mutate(name = str_replace(name,
                            "California State University,[[:space:]]",
                            "California State University-")) %>%

  left_join(Basic2021, 
            keep = TRUE )

# how many schools did we match with the CC data
uni_name %>% 
  filter(!is.na(basic2021)) %>% 
  nrow() # 245, 290, 300, 313, 404 / 433 for US unis

# which schools don't match with the CC data?
uni_name %>% 
  select(name.x, name.y)  %>% 
  filter(is.na(name.y)) %>% 
  distinct()

uni_name_tally <- 
uni_name %>% 
  left_join(CC,
            join_by("basic2021" == "Value")) %>% 
  group_by(Category) %>% 
  tally(sort = TRUE) %>% 
  drop_na()

ggplot(uni_name_tally) +
  aes(reorder(Category, n), n) +
  geom_col() +
  coord_flip() +
  xlab("") +
  theme_minimal(base_size = 14)
